Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/10-introduction.tex
Updates from Overleaf

% General context + scope limitation
OCRed texts are generally not sufficient to build a high level, semantic view of a collection of historical documents.
A subsequent stage is often needed to extract the pieces of information most likely to be searched for by users, such as named entities: people, organisations, dates, places, etc.
Indeed, being able to properly tag text tokens unlocks the ability to relate entities, and provide colleagues from other fields with databases ready for exploitation.

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due to multiple causes related to text readability (low resolution scans, inconsistent printing rules, artefacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts, and also from the errors introduced into the text by the OCR step.

In this article, we focus on a peculiar category of historical printed books: city trade directories of Paris from the XIX\textsuperscript{th} century (1801 - 1854).
They contain hundred-pages long lists of people, along with their activity and their address, and provide valuable fine-grained knowledge to study the social dynamics of the city over time.
Despite containing roughly the same information, the diversity in layouts, information organisation and digitising quality is challenging both for OCR and NER.

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extracts texts with OCR, identifies directories entries and recognises business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from Parisian trade directories.
Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches to assess their usability on the corpus.

>>>>

% General context + scope limitation
OCRed texts are generally not sufficient to build a high level semantic view of a collection of historical documents.
A subsequent stage is often needed to extract the pieces of information most likely to be searched for by users, such as named entities: persons, organisations, dates, places, etc.
Indeed, being able to properly tag text tokens unlocks the ability to relate entities and provide colleagues from other fields with databases ready for exploitation.

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due to multiple causes related to text readability (low resolution scans, inconsistent printing rules, artefacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the great diversity of historical sources.
On the other hand, the semantics of entities in NER approaches developed for modern texts may be different from those in ancient texts.

In this article, we focus on a corpus of printed trade directories of Paris from the XIX\textsuperscript{th} century, containing hundreds of pages long lists of people with their activity and address.
They provide fine-grained knowledge to study the social dynamics of the city over time.
As they originate from different publishers, they show a diversity in layout, information organisation and printing quality, which adds to the poor digitising quality to make OCR and NER challenging tasks.

Trade directories have been leveraged in a recent work to identify polluted urban soils \cite{bell2020automated} and locate all gas stations in the city of Providence over the last century.
In an ongoing research project we aim at producing structured spatio-temporal data from the entries in the Paris trade directories to study the transformations of the fraction of XIX\textsuperscript{th} century Parisian society reachable through these sources.
%Because they originate from several publishers, their content is organised following different indexing methods (by name, by activity or by address), is printed in various layouts, and uses different fonts.
Therefor, we investigate several state-of-the-art OCR and NER approaches to assess their usability to process the corpus.

### 2022-01-20 src-latex/parts/30-dataset.tex
Updates from Overleaf

The directories to be processed are stored in different libraries in Paris. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).

@@

For training as testing purposes, our groundtruth dataset must be as representative as possible of the diversity of the available directories.

For example, the Didot directory of 1854 is organised according to three indexes: by name, by activity, and by street name. The structure of the following entry is characteristic of its index by name: "Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47." This entry begins with a person's name, followed by the initials of their first name in parentheses.The symbol indicates that this person was awarded the Légion d'Honneur. The following part of this entry represents the person's activity,i.e. their profession, or social status, here "professor at the Conservatory of music and declamation". The street name and number where the person lives or carries out their activity are written at the end of the entry.

These pieces of information constituting the structure of the entries are the basic data that we want to extract, deduplicate and structure in order to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. With the exception of some potentially wordy activity descriptions, they correspond to named entities. However, as Table \ref{tab:directories} shows, while most entries contain the same types of named entities, their order and the way they are written vary from one directory or index to another. To provide examples of each entry structure, pages from each type have thus been annotated\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Scheme of the data extraction pipeline with two quality control checkpoints. \joseph{Missing "Ground truth" for NER stage?}}
    \label{fig.pipeline}
\end{figure}

@@

The simplified data extraction pipeline depicted in~\cref{fig.pipeline} processes the documents presented
in~\cref{sec:dataset}. First, the layout extraction and entry segmentation of the page are performed with a
semi-automated system and checked by a human. The resulting images, representing 8765 entries, are the inputs of a customizable two-stage pipeline.

>>>>

The directories to be processed are stored in different libraries in Paris. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}). For training and testing purposes, our groundtruth dataset must be as representative as possible of the diversity of the available directories.

@@

For example, the Didot directory of 1854 is organised according to three indexes: by name, by activity, and by street name. The structure of the following entry is characteristic of its index by name: "Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47." This entry begins with a person's name, followed by the initials of their first name in parentheses.The symbol indicates that this person was awarded the Légion d'Honneur. The following part of this entry represents the person's activity,i.e., their profession, or social status, here "professor at the Conservatory of music and declamation". The street name and number where the person lives or carries out their activities are written at the end of the entry.

These pieces of information constituting the structure of the entries are the basic data that we want to extract, deduplicate, and structure to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory or index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/protocol.pdf}
    \caption{Data extraction pipeline with two quality control checkpoints. }
    \label{fig.pipeline}
\end{figure}

@@

The simplified data extraction pipeline depicted in~\cref{fig.pipeline} processes the documents presented
in~\cref{sec:dataset}. First, the page layout extraction and entry segmentation are performed with a
semi-automated system and checked by a human. The resulting images, representing 8765 entries, are the inputs of a customizable two-stage pipeline.
